---
title: "Proteomic Consistency Metrics"
author: "Simina Boca, Shaojun Tang, Yi Bai, Jiahao Huang, Nathan Edwards"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
params:
  qcmetricsfile: inputfilename.tsv
  format: html_document
output:
  html_document:
    number_sections: yes
    smooth_scroll: no
    toc: yes
    toc_depth: 3
    toc_float: yes
  pdf_document:
    number_sections: yes
    toc: yes
always_allow_html: yes
---

<!--Resize the main-container to spread the title-->
<style>
body .main-container {
max-width: 2030px;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE)
```

```{r, warning=FALSE, include=FALSE}
library(ggplot2)
library(reshape2)
library(knitr)
library(kableExtra)
library(RColorBrewer) ## generate palette
library(grid)
library(pander) ## this package is used ot convert the .md file into PDF
suppressPackageStartupMessages(library(dplyr))
suppressPackageStartupMessages(library(gridExtra)) ## to show the plots side by side 
suppressPackageStartupMessages(library(plotly))
options(warn = -1)
```

```{r}
# this allows the kable function work in html format to make pretty tables
#but will not work in the PDF files, remember to remove it if generating PDF files
#also remving the lines with kable in the code chunks related
if (params$format != 'pdf_document') {
  options(knitr.table.format = "html")  
}
```

```{r,include=FALSE}
##Read in metrics for individual analytical samples and fractions and check number of fractions and samples

# files <- list.files(".")
# files <- list.files("d:/research/Collaborations/CPTAC/mzML/SourceCode/")  # (".")

# Load from the Input forder (Jiahao)
files <- list.files("./Input")


# QCmetrics_file <- files[grep("tsv",files)]

# QCmetrics <- read.table(paste0("d:/research/Collaborations/CPTAC/mzML/SourceCode/", QCmetrics_file), header=TRUE, sep="\t")

# Current Working Metrics (Jiahao)
QCmetrics_file <- files[grep("CPTAC3_Uterine_Corpus_Endometrial_Carcinoma_Proteome.qcmetrics.tsv",files)]
Summary_file <- files[grep("CPTAC3_Uterine_Corpus_Endometrial_Carcinoma_Proteome.summary.tsv",files)]
tmt10_file <- files[grep("CPTAC3_Uterine_Corpus_Endometrial_Carcinoma_Proteome.tmt10.tsv",files)]

#QCmetrics_file <- files[grep("CPTAC3_Clear_Cell_Renal_Cell_Carcinoma_Proteome.qcmetrics.tsv",files)]
#Summary_file <- files[grep("CPTAC3_Clear_Cell_Renal_Cell_Carcinoma_Proteome.summary.tsv",files)]
#tmt10_file <- files[grep("CPTAC3_Clear_Cell_Renal_Cell_Carcinoma_Proteome.tmt10.tsv",files)]

#QCmetrics_file <- params$qcmetricsfile
#QCmetrics <- read.table(QCmetrics_file, header=TRUE, sep="\t")
QCmetrics <- read.table(paste0("~/Desktop/CPTAC_3 /Input/", QCmetrics_file), header=TRUE, sep="\t")
SUmetrics <- read.table(paste0("~/Desktop/CPTAC_3 /Input/", Summary_file), header=TRUE, sep="\t", quote = "")

# dim(QCmetrics)
# head(QCmetrics)

##rename "fractionNum" to "Fraction"
QCmetrics <- rename(QCmetrics, Fraction=fractionNum)

QCmetrics$analyticalBasenameLabel <- QCmetrics$analyticalBasename
QCmetrics$analyticalBasenameFactor <- factor(QCmetrics$analyticalBasenameLabel)
QCmetrics$analyticalBasenameIndex <- as.numeric(QCmetrics$analyticalBasenameFactor)
QCmetrics$analyticalBasename <- QCmetrics$analyticalBasenameIndex

# if these are left as numbers, the color scale is messed up. Why?
# QCmetrics$analyticalBasename <- as.character(QCmetrics$analyticalBasename)
# This will ensure proper sort order (at least until 100 analytical samples)
QCmetrics$analyticalBasename <- sprintf("%02d",QCmetrics$analyticalBasename)

##add some new columns to QCmetrics (same as other columns, but useful for tooltip!)
QCmetrics$`Analytical sample` <- QCmetrics$analyticalBasename 

# summary(QCmetrics$analyticalBasename)
# summary(QCmetrics$analyticalBasenameIndex)

##get total number of spectra per analytical sample
numofMS2_ALL_per_AS <- tapply(QCmetrics$numofMS2_ALL, INDEX=QCmetrics$analyticalBasename, FUN=sum)
numofMS2_ID_per_AS <- tapply(QCmetrics$numofMS2_ID, INDEX=QCmetrics$analyticalBasename, FUN=sum)
identical(names(numofMS2_ALL_per_AS), names(numofMS2_ID_per_AS))

QCmetrics_AS <- data.frame(analyticalBasename=names(numofMS2_ID_per_AS),
                           numofMS2_ALL_per_AS=numofMS2_ALL_per_AS,
                           numofMS2_ID_per_AS=numofMS2_ID_per_AS)
QCmetrics_AS$`Analytical sample` <- QCmetrics_AS$analyticalBasename
```

```{r,include=FALSE}
##need to separate out the fractions if they are all equal to NA (this means they have not been pulled out before)
if(sum(!is.na(QCmetrics$Fraction)) == 0)
{
  analyticalBasenameSplit <- strsplit(as.character(QCmetrics$analyticalBasename),"_Fr_")
  QCmetrics$analyticalBasename <- sapply(analyticalBasenameSplit, function(x){x[1]})
  QCmetrics$Fraction <- as.numeric(sapply(analyticalBasenameSplit, function(x){x[2]}))
  unique(QCmetrics$Fraction)
  QCmetrics$Fraction[is.na(QCmetrics$Fraction)] <- 25
}

##Get the fractions (check they are 1-24):
##Ugh - should use a better marker for "A" - how about 1000? or -1? or #unique fraction values? 
##QCmetrics file will have an A in the fraction position, not NA, from now on. Handle this explicitly. 

sort(unique(QCmetrics$Fraction))
length(unique(QCmetrics$Fraction))

QCmetrics$Fraction[is.na(QCmetrics$Fraction)] <- 25
```

```{r, include=FALSE}
##Get the number of unique analytical samples

analyticalSamples <- unique(QCmetrics$analyticalBasename)
length(analyticalSamples)

##Make sure the labels in spectrumBasename are unique

length(unique(QCmetrics$spectrumBasename))

##Get the number of unique fractions
fractions <- unique(QCmetrics$Fraction)
```

```{r,include=FALSE}
##Change some column names to make things easier
QCmetrics <- rename(QCmetrics,
                    PrecursorIntensityALL.0 = minPrecursorIntensity_ALL,
                    PrecursorIntensityALL.5 = PrecursorIntensity5perc_ALL,
                    PrecursorIntensityALL.25 = PrecursorIntensity25perc_ALL,
                    PrecursorIntensityALL.50 = PrecursorIntensity50perc_ALL,
                    PrecursorIntensityALL.75 = PrecursorIntensity75perc_ALL,
                    PrecursorIntensityALL.95 = PrecursorIntensity95perc_ALL,
                    PrecursorIntensityALL.100 = maxPrecursorIntensity_ALL)
QCmetrics <- rename(QCmetrics,
                    PrecursorMZALL.0 = minPrecursorMZ_ALL,
                    PrecursorMZALL.5 = PrecursorMZ5perc_ALL,
                    PrecursorMZALL.25 = PrecursorMZ25perc_ALL,
                    PrecursorMZALL.50 = PrecursorMZ50perc_ALL,
                    PrecursorMZALL.75 = PrecursorMZ75perc_ALL,
                    PrecursorMZALL.95 = PrecursorMZ95perc_ALL,
                    PrecursorMZALL.100 = maxPrecursorMZ_ALL)

QCmetrics <- rename(QCmetrics,
                    PrecursorMWALL.0 = minPrecursorMW_ALL,
                    PrecursorMWALL.5 = PrecursorMW5perc_ALL,
                    PrecursorMWALL.25 = PrecursorMW25perc_ALL,
                    PrecursorMWALL.50 = PrecursorMW50perc_ALL,
                    PrecursorMWALL.75 = PrecursorMW75perc_ALL,
                    PrecursorMWALL.95 = PrecursorMW95perc_ALL,
                    PrecursorMWALL.100 = maxPrecursorMW_ALL)

QCmetrics <- rename(QCmetrics,
                    MS2perMS1ALL.0 = minMS2perMS1_ALL,
                    MS2perMS1ALL.5 = MS2perMS1_5perc_ALL,
                    MS2perMS1ALL.25 = MS2perMS1_25perc_ALL,
                    MS2perMS1ALL.50 = MS2perMS1_50perc_ALL,
                    MS2perMS1ALL.75 = MS2perMS1_75perc_ALL,
                    MS2perMS1ALL.95 = MS2perMS1_95perc_ALL,
                    MS2perMS1ALL.100 = maxMS2perMS1_ALL)
QCmetrics <- rename(QCmetrics,
                    MS2chargeALL.1 = MS2Charge1_ALL,
                    MS2chargeALL.2 = MS2Charge2_ALL,
                    MS2chargeALL.3 = MS2Charge3_ALL,
                    MS2chargeALL.4 = MS2Charge4_ALL,
                    MS2chargeALL.5andhigher = MS2Charge5_ALL##MS2Charge5andHigher_ALL,
                   )
## Adding Redundancy (Jiahao)
QCmetrics <- rename(QCmetrics,
                    PeptideRd.0 = minPeptideRedundancy,
                    PeptideRd.5 = PeptideRedundancy5perc,
                    PeptideRd.25 = PeptideRedundancy25perc,
                    PeptideRd.50 = PeptideRedundancy50perc,
                    PeptideRd.75 = PeptideRedundancy75perc,
                    PeptideRd.95 = PeptideRedundancy95perc,
                    PeptideRd.100 = maxPeptideRedundancy)

# Adding Retention Time ALL
QCmetrics <- rename(QCmetrics,
                    RetentionTimeALL.0 = minRetentionTime_ALL,
                    RetentionTimeALL.5 = RetentionTime5perc_ALL,
                    RetentionTimeALL.25 = RetentionTime25perc_ALL,
                    RetentionTimeALL.50 = RetentionTime50perc_ALL,
                    RetentionTimeALL.75 = RetentionTime75perc_ALL,
                    RetentionTimeALL.95 = RetentionTime95perc_ALL,
                    RetentionTimeALL.100 = maxRetentionTime_ALL)


charge0avail <- FALSE
if ("MS2Charge0_ALL" %in% colnames(QCmetrics)) {
    QCmetrics <- rename(QCmetrics,
                        MS2chargeALL.0 = MS2Charge0_ALL)
    charge0avail <- TRUE
}

##Create data frame melting the precursor intensities
QCmetricsLongPrecInt_ALL <- melt(QCmetrics[,c(2,3,grep("PrecursorIntensityALL.",colnames(QCmetrics)))],
                             variable.name="PrecursorIntensityALL",
                             value.name="value",
                             id.vars=c("analyticalBasename","Fraction"))
head(QCmetricsLongPrecInt_ALL)
QCmetricsLongPrecInt_ALL <- cbind(QCmetricsLongPrecInt_ALL[,1:2],
                              colsplit(QCmetricsLongPrecInt_ALL[,3], "\\.",
                                       c("PrecursorIntensityALL","Percentile")),
                              QCmetricsLongPrecInt_ALL[,4])
head(QCmetricsLongPrecInt_ALL)
colnames(QCmetricsLongPrecInt_ALL)[5] <- "value"

QCmetricsLongPrecInt_ALL$`Analytical sample` <- QCmetricsLongPrecInt_ALL$analyticalBasename
QCmetricsLongPrecInt_ALL$Fraction <- QCmetricsLongPrecInt_ALL$Fraction

##Create data frame melting the precursor MZ values
QCmetricsLongPrecMZ_ALL <- melt(QCmetrics[,c(2,3,grep("PrecursorMZALL.",colnames(QCmetrics)))],
                            variable.name="PrecursorMZALL",
                            value.name="value",
                            id.vars=c("analyticalBasename","Fraction"))
head(QCmetricsLongPrecMZ_ALL)
QCmetricsLongPrecMZ_ALL <- cbind(QCmetricsLongPrecMZ_ALL[,1:2],
                             colsplit(QCmetricsLongPrecMZ_ALL[,3], "\\.",
                                      c("PrecursorMZALL","Percentile")),
                             QCmetricsLongPrecMZ_ALL[,4])
head(QCmetricsLongPrecMZ_ALL)
colnames(QCmetricsLongPrecMZ_ALL)[5] <- "value"

QCmetricsLongPrecMZ_ALL$`Analytical sample` <- QCmetricsLongPrecMZ_ALL$analyticalBasename
QCmetricsLongPrecMZ_ALL$Fraction <- QCmetricsLongPrecMZ_ALL$Fraction

##Create data frame melting the precursor MW values
QCmetricsLongPrecMW_ALL <- melt(QCmetrics[,c(2,3,grep("PrecursorMWALL.",colnames(QCmetrics)))],
                            variable.name="PrecursorMWALL",
                            value.name="value",
                            id.vars=c("analyticalBasename","Fraction"))
head(QCmetricsLongPrecMW_ALL)
QCmetricsLongPrecMW_ALL <- cbind(QCmetricsLongPrecMW_ALL[,1:2],
                             colsplit(QCmetricsLongPrecMW_ALL[,3], "\\.",
                                      c("PrecursorMWALL","Percentile")),
                             QCmetricsLongPrecMW_ALL[,4])
head(QCmetricsLongPrecMW_ALL)
colnames(QCmetricsLongPrecMW_ALL)[5] <- "value"

QCmetricsLongPrecMW_ALL$`Analytical sample` <- QCmetricsLongPrecMW_ALL$analyticalBasename
QCmetricsLongPrecMW_ALL$Fraction <- QCmetricsLongPrecMW_ALL$Fraction

##Create data frame melting the MS2perMS values
QCmetricsLongMS2perMS_ALL <- melt(QCmetrics[,c(2,3,grep("MS2perMS1ALL.",colnames(QCmetrics)))],
                              variable.name=" MS2perMS1ALL",
                            value.name="value",
                              id.vars=c("analyticalBasename","Fraction"))
head(QCmetricsLongMS2perMS_ALL)
QCmetricsLongMS2perMS_ALL <- cbind(QCmetricsLongMS2perMS_ALL[,1:2],
                               colsplit(QCmetricsLongMS2perMS_ALL[,3], "\\.",
                                        c("MS2perMS1ALL","Percentile")),
                               QCmetricsLongMS2perMS_ALL[,4])
head(QCmetricsLongMS2perMS_ALL)
colnames(QCmetricsLongMS2perMS_ALL)[5] <- "value"

QCmetricsLongMS2perMS_ALL$`Analytical sample` <- QCmetricsLongMS2perMS_ALL$analyticalBasename
QCmetricsLongMS2perMS_ALL$Fraction <- QCmetricsLongMS2perMS_ALL$Fraction

##Create data frame melting MS2 charge ratio
QCmetricsLongMS2Charge_ALL <- melt(QCmetrics[,c(2,3,grep("MS2chargeALL.",colnames(QCmetrics)))],
                                    variable.name="MS2chargeALL",
                                    value.name="value",
                                    id.vars=c("analyticalBasename","Fraction"))
head(QCmetricsLongMS2Charge_ALL)
QCmetricsLongMS2Charge_ALL <- cbind(QCmetricsLongMS2Charge_ALL[,1:2],
                                     colsplit(QCmetricsLongMS2Charge_ALL[,3], "\\.", c("MS2chargeALL","MS2ChargeState")),
                                     QCmetricsLongMS2Charge_ALL[,4])
head(QCmetricsLongMS2Charge_ALL)
colnames(QCmetricsLongMS2Charge_ALL)[5] <- "value"
QCmetricsLongMS2Charge_ALL$MS2chargeALL <- NULL
totalMS2_ALL = sum(QCmetricsLongMS2Charge_ALL$value)
QCmetricsLongMS2Charge_ALL$Chargeratio<- c(QCmetricsLongMS2Charge_ALL$value/totalMS2_ALL)

QCmetricsLongMS2Charge_ALL$`Analytical sample` <- QCmetricsLongMS2Charge_ALL$analyticalBasename
QCmetricsLongMS2Charge_ALL$Fraction <- QCmetricsLongMS2Charge_ALL$Fraction

# Create data frame melting Peptie Redundancy (Jiahao)
QCmetricsPeptideRd <- melt(QCmetrics[,c(2,3,grep("PeptideRd.",colnames(QCmetrics)))],
                            variable.name="PeptideRd",
                            value.name="value",
                            id.vars=c("analyticalBasename","Fraction"))
head(QCmetricsPeptideRd)
QCmetricsPeptideRd <- cbind(QCmetricsPeptideRd[,1:2],
                             colsplit(QCmetricsPeptideRd[,3], "\\.",
                                      c("PeptideRd","Percentile")),
                             QCmetricsPeptideRd[,4])
head(QCmetricsPeptideRd)
colnames(QCmetricsPeptideRd)[5] <- "value"

QCmetricsPeptideRd$`Analytical sample` <- QCmetricsPeptideRd$analyticalBasename
QCmetricsPeptideRd$Fraction <- QCmetricsPeptideRd$Fraction

# Create data frame melting Retention Time All
QCmetricsPeptideRT_ALL <- melt(QCmetrics[,c(2,3,grep("RetentionTimeALL.",colnames(QCmetrics)))],
                            variable.name="RetentionTimeALL",
                            value.name="value",
                            id.vars=c("analyticalBasename","Fraction"))
head(QCmetricsPeptideRT_ALL)
QCmetricsPeptideRT_ALL <- cbind(QCmetricsPeptideRT_ALL[,1:2],
                             colsplit(QCmetricsPeptideRT_ALL[,3], "\\.",
                                      c("RetentionTimeALL","Percentile")),
                             QCmetricsPeptideRT_ALL[,4])
head(QCmetricsPeptideRT_ALL)
colnames(QCmetricsPeptideRT_ALL)[5] <- "value"

QCmetricsPeptideRT_ALL$`Analytical sample` <- QCmetricsPeptideRT_ALL$analyticalBasename
QCmetricsPeptideRT_ALL$Fraction <- QCmetricsPeptideRT_ALL$Fraction

# Create dataframe for different charge state
# create the label

if (charge0avail) {
  chargestate <- c("N/A","+1","+2", "+3","+4","5 and Higher")
} else {
  chargestate <- c("+1","+2", "+3","+4","5 and Higher")
}

#calculate the ratio for each of the charge state   
chargestateratio_ALL <- 
  c(sum(subset(QCmetricsLongMS2Charge_ALL, 
               MS2ChargeState == 1,select=c(Chargeratio))), 
    sum(subset(QCmetricsLongMS2Charge_ALL, 
               MS2ChargeState == 2,select=c(Chargeratio))), 
    sum(subset(QCmetricsLongMS2Charge_ALL, 
               MS2ChargeState == 3,select=c(Chargeratio))), 
    sum(subset(QCmetricsLongMS2Charge_ALL, 
               MS2ChargeState == 4,select=c(Chargeratio))), 
    sum(subset(QCmetricsLongMS2Charge_ALL, 
               MS2ChargeState == "5andhigher",select=c(Chargeratio))))

if (charge0avail) {
  chargestateratio_ALL <- c(sum(subset(QCmetricsLongMS2Charge_ALL,                                                                       MS2ChargeState == 0,select=c(Chargeratio))),chargestateratio_ALL)
}

#generate the data frame contains the cahrge ratio
Chargeratio_ALL <- data.frame(chargestate, chargestateratio_ALL)
```

```{r,include=FALSE}
##Change some column names to make things easier
QCmetrics <- rename(QCmetrics,
                    PrecursorIntensityID.0 = minPrecursorIntensity_ID,
                    PrecursorIntensityID.5 = PrecursorIntensity5perc_ID,
                    PrecursorIntensityID.25 = PrecursorIntensity25perc_ID,
                    PrecursorIntensityID.50 = PrecursorIntensity50perc_ID,
                    PrecursorIntensityID.75 = PrecursorIntensity75perc_ID,
                    PrecursorIntensityID.95 = PrecursorIntensity95perc_ID,
                    PrecursorIntensityID.100 = maxPrecursorIntensity_ID)
QCmetrics <- rename(QCmetrics,
                    PrecursorMZID.0 = minPrecursorMZ_ID,
                    PrecursorMZID.5 = PrecursorMZ5perc_ID,
                    PrecursorMZID.25 = PrecursorMZ25perc_ID,
                    PrecursorMZID.50 = PrecursorMZ50perc_ID,
                    PrecursorMZID.75 = PrecursorMZ75perc_ID,
                    PrecursorMZID.95 = PrecursorMZ95perc_ID,
                    PrecursorMZID.100 = maxPrecursorMZ_ID)

QCmetrics <- rename(QCmetrics,
                    PrecursorMWID.0 = minPrecursorMW_ID,
                    PrecursorMWID.5 = PrecursorMW5perc_ID,
                    PrecursorMWID.25 = PrecursorMW25perc_ID,
                    PrecursorMWID.50 = PrecursorMW50perc_ID,
                    PrecursorMWID.75 = PrecursorMW75perc_ID,
                    PrecursorMWID.95 = PrecursorMW95perc_ID,
                    PrecursorMWID.100 = maxPrecursorMW_ID)

QCmetrics <- rename(QCmetrics,
                    MS2perMS1ID.0 = minMS2perMS1_ID,
                    MS2perMS1ID.5 = MS2perMS1_5perc_ID,
                    MS2perMS1ID.25 = MS2perMS1_25perc_ID,
                    MS2perMS1ID.50 = MS2perMS1_50perc_ID,
                    MS2perMS1ID.75 = MS2perMS1_75perc_ID,
                    MS2perMS1ID.95 = MS2perMS1_95perc_ID,
                    MS2perMS1ID.100 = maxMS2perMS1_ID)
QCmetrics <- rename(QCmetrics,
                    MS2chargeID.1 = MS2Charge1_ID,
                    MS2chargeID.2 = MS2Charge2_ID,
                    MS2chargeID.3 = MS2Charge3_ID,
                    MS2chargeID.4 = MS2Charge4_ID,
                    MS2chargeID.5andhigher = MS2Charge5_ID##MS2Charge5andHigher_ID,
                   )

# Adding Retention Time ID (Jiahao)
QCmetrics <- rename(QCmetrics,
                    RetentionTimeID.0 = minRetentionTime_ID,
                    RetentionTimeID.5 = RetentionTime5perc_ID,
                    RetentionTimeID.25 = RetentionTime25perc_ID,
                    RetentionTimeID.50 = RetentionTime50perc_ID,
                    RetentionTimeID.75 = RetentionTime75perc_ID,
                    RetentionTimeID.95 = RetentionTime95perc_ID,
                    RetentionTimeID.100 = maxRetentionTime_ID)


if ("MS2Charge0_ID" %in% colnames(QCmetrics)) {
    QCmetrics <- rename(QCmetrics,
                        MS2chargeID.0 = MS2Charge0_ID)
}


##Create data frame melting the precursor intensities
QCmetricsLongPrecInt_ID <- melt(QCmetrics[,c(2,3,grep("PrecursorIntensityID.",colnames(QCmetrics)))],
                             variable.name="PrecursorIntensityID",
                             value.name="value",
                             id.vars=c("analyticalBasename","Fraction"))
head(QCmetricsLongPrecInt_ID)
QCmetricsLongPrecInt_ID <- cbind(QCmetricsLongPrecInt_ID[,1:2],
                              colsplit(QCmetricsLongPrecInt_ID[,3], "\\.",
                                       c("PrecursorIntensityID","Percentile")),
                              QCmetricsLongPrecInt_ID[,4])
head(QCmetricsLongPrecInt_ID)
colnames(QCmetricsLongPrecInt_ID)[5] <- "value"

QCmetricsLongPrecInt_ID$`Analytical sample` <- QCmetricsLongPrecInt_ID$analyticalBasename
QCmetricsLongPrecInt_ID$Fraction <- QCmetricsLongPrecInt_ID$Fraction

##Create data frame melting the precursor MZ values
QCmetricsLongPrecMZ_ID <- melt(QCmetrics[,c(2,3,grep("PrecursorMZID.",colnames(QCmetrics)))],
                            variable.name="PrecursorMZID",
                            value.name="value",
                            id.vars=c("analyticalBasename","Fraction"))
head(QCmetricsLongPrecMZ_ID)
QCmetricsLongPrecMZ_ID <- cbind(QCmetricsLongPrecMZ_ID[,1:2],
                             colsplit(QCmetricsLongPrecMZ_ID[,3], "\\.",
                                      c("PrecursorMZID","Percentile")),
                             QCmetricsLongPrecMZ_ID[,4])
head(QCmetricsLongPrecMZ_ID)
colnames(QCmetricsLongPrecMZ_ID)[5] <- "value"

QCmetricsLongPrecMZ_ID$`Analytical sample` <- QCmetricsLongPrecMZ_ID$analyticalBasename
QCmetricsLongPrecMZ_ID$Fraction <- QCmetricsLongPrecMZ_ID$Fraction

##Create data frame melting the precursor MW values
QCmetricsLongPrecMW_ID <- melt(QCmetrics[,c(2,3,grep("PrecursorMWID.",colnames(QCmetrics)))],
                            variable.name="PrecursorMWID",
                            value.name="value",
                            id.vars=c("analyticalBasename","Fraction"))
head(QCmetricsLongPrecMW_ID)
QCmetricsLongPrecMW_ID <- cbind(QCmetricsLongPrecMW_ID[,1:2],
                             colsplit(QCmetricsLongPrecMW_ID[,3], "\\.",
                                      c("PrecursorMWID","Percentile")),
                             QCmetricsLongPrecMW_ID[,4])
head(QCmetricsLongPrecMW_ID)
colnames(QCmetricsLongPrecMW_ID)[5] <- "value"

QCmetricsLongPrecMW_ID$`Analytical sample` <- QCmetricsLongPrecMW_ID$analyticalBasename
QCmetricsLongPrecMW_ID$Fraction <- QCmetricsLongPrecMW_ID$Fraction


##Create data frame melting the MS2perMS values
QCmetricsLongMS2perMS_ID <- melt(QCmetrics[,c(2,3,grep("MS2perMS1ID.",colnames(QCmetrics)))],
                              variable.name=" MS2perMS1",
                              value.name="value",
                              id.vars=c("analyticalBasename","Fraction"))
head(QCmetricsLongMS2perMS_ID)
QCmetricsLongMS2perMS_ID <- cbind(QCmetricsLongMS2perMS_ID[,1:2],
                               colsplit(QCmetricsLongMS2perMS_ID[,3], "\\.",
                                        c("MS2perMS1ID","Percentile")),
                               QCmetricsLongMS2perMS_ID[,4])
head(QCmetricsLongMS2perMS_ID)
colnames(QCmetricsLongMS2perMS_ID)[5] <- "value"

QCmetricsLongMS2perMS_ID$`Analytical sample` <- QCmetricsLongMS2perMS_ID$analyticalBasename
QCmetricsLongMS2perMS_ID$Fraction <- QCmetricsLongMS2perMS_ID$Fraction

##Create data frame melting MS2 charge ratio
QCmetricsLongMS2Charge_ID <- melt(QCmetrics[,c(2,3,grep("MS2chargeID.",colnames(QCmetrics)))],
                                    variable.name="MS2chargeID",
                                    value.name="value",
                                    id.vars=c("analyticalBasename","Fraction"))
head(QCmetricsLongMS2Charge_ID)
QCmetricsLongMS2Charge_ID <- cbind(QCmetricsLongMS2Charge_ID[,1:2],
                                     colsplit(QCmetricsLongMS2Charge_ID[,3], "\\.", c("MS2chargeID","MS2ChargeState")),
                                     QCmetricsLongMS2Charge_ID[,4])
head(QCmetricsLongMS2Charge_ID)
colnames(QCmetricsLongMS2Charge_ID)[5] <- "value"
QCmetricsLongMS2Charge_ID$MS2chargeID <- NULL
totalMS2_ID = sum(QCmetricsLongMS2Charge_ID$value)
QCmetricsLongMS2Charge_ID$Chargeratio<- c(QCmetricsLongMS2Charge_ID$value/totalMS2_ID)

QCmetricsLongMS2Charge_ID$`Analytical sample` <- QCmetricsLongMS2Charge_ID$analyticalBasename
QCmetricsLongMS2Charge_ID$Fraction <- QCmetricsLongMS2Charge_ID$Fraction

# calculate the values for charge distribution for differnt cahrge state 
chargestateratio_ID <- c(sum(subset(QCmetricsLongMS2Charge_ID, MS2ChargeState == 1,select=c(Chargeratio))), sum(subset(QCmetricsLongMS2Charge_ID, MS2ChargeState == 2,select=c(Chargeratio))), sum(subset(QCmetricsLongMS2Charge_ID, MS2ChargeState == 3,select=c(Chargeratio))), sum(subset(QCmetricsLongMS2Charge_ID, MS2ChargeState == 4,select=c(Chargeratio))), sum(subset(QCmetricsLongMS2Charge_ID, MS2ChargeState == "5andhigher",select=c(Chargeratio))))
if (charge0avail) {
  chargestateratio_ID <- c(sum(subset(QCmetricsLongMS2Charge_ID,                                                                       MS2ChargeState == 0,select=c(Chargeratio))),chargestateratio_ID)
}

#generate the data frame contains the cahrge ratio (Jiahao)
Chargeratio_ID <- data.frame(chargestate, chargestateratio_ID)
Chargeratio_ID$`Proportion` <- round((Chargeratio_ID$chargestateratio_ID)*100,2)
Chargeratio_ALL$`Proportion` <- round((Chargeratio_ALL$chargestateratio_ALL)*100,2)

summary(Chargeratio_ALL)
summary(Chargeratio_ID)

# Create data frame melting Retention Time ID (Jiahao)
QCmetricsPeptideRT_ID <- melt(QCmetrics[,c(2,3,grep("RetentionTimeID.",colnames(QCmetrics)))],
                            variable.name="RetentionTimeID",
                            value.name="value",
                            id.vars=c("analyticalBasename","Fraction"))
head(QCmetricsPeptideRT_ID)
QCmetricsPeptideRT_ID <- cbind(QCmetricsPeptideRT_ID[,1:2],
                             colsplit(QCmetricsPeptideRT_ID[,3], "\\.",
                                      c("RetentionTimeID","Percentile")),
                             QCmetricsPeptideRT_ID[,4])
head(QCmetricsPeptideRT_ID)
colnames(QCmetricsPeptideRT_ID)[5] <- "value"

QCmetricsPeptideRT_ID$`Analytical sample` <- QCmetricsPeptideRT_ID$analyticalBasename
QCmetricsPeptideRT_ID$Fraction <- QCmetricsPeptideRT_ID$Fraction
```

```{r, include=FALSE}
# Cleaning the Summary data
col_selection <- grepl(".Unshared.Peptides$", names(SUmetrics))
Spectral_table <- SUmetrics[col_selection]

id_protein <- Spectral_table[,] >= 2
id_protein <- data.frame(colSums(id_protein))
colnames(id_protein) <- "ProteinCounts"
id_protein$analyticalBasename <- rownames(id_protein)

id_protein$analyticalBasenameLabel <- id_protein$analyticalBasename
id_protein$analyticalBasenameFactor <- factor(id_protein$analyticalBasenameLabel)
id_protein$analyticalBasenameIndex <- as.numeric(id_protein$analyticalBasenameFactor)
id_protein$analyticalBasename <- id_protein$analyticalBasenameIndex
 
id_protein$analyticalBasename <- as.character(id_protein$analyticalBasename)
id_protein$analyticalBasename <- sprintf("%02s",id_protein$analyticalBasename)
id_protein$`Analytical sample` <- id_protein$analyticalBasename

total_p <- nrow(Spectral_table)
```

```{r, include=FALSE}
# Cleaning the TMT10 data
raw_edata <- read.table(paste0("~/Desktop/CPTAC_3 /Input/", tmt10_file), header=TRUE, sep="\t", row.names=1, quote="")

# Subset the raw metrics 
s_selection <- grepl("^(?=.*Log.Ratio)(?!.*Unshared)", names(raw_edata), perl = TRUE)
#us_selection <- grepl(".Unshared.Log.Ratio$", names(raw_edata))

s_metrics <- tail(raw_edata[,s_selection], -3)

# Clean the metrics (remove NAs in s_metrics, keep ref_metrics as reference)
ref_metrics <- s_metrics
s_metrics <- s_metrics[complete.cases(s_metrics),]
#us_metrics <- us_metrics[complete.cases(us_metrics),]

# Construct pheno metrics (s_metrics)
s_sample <- colnames(s_metrics)
s_x <- c(1:(ncol(s_metrics)/9))
s_batch <- rep(s_x, each=9)
s_pheno <- data.frame(s_sample, s_batch, row.names=1)
s_pheno$s_batch <- sprintf("%02d",s_pheno$s_batch)
batch = as.factor(s_pheno$s_batch)
#View(s_pheno)

# Compute NAs in ref_metrics for PCA
for(i in 1:nrow(ref_metrics)){
  ref_metrics[i, is.na(ref_metrics[i,])] <- min(ref_metrics[i,], na.rm = TRUE)
}
```

```{r,include=FALSE}
# generating a color Palettes for ggvis 
# plotColorPalettes is the function for generating the pallettes, the colors in the palettes depends on the number we put in 
# in our case, the palettes is called plotcolor

plotColorPalettes <- function(g){
  d <- 360/g
  h <- cumsum(c(15, rep(d,g - 1)))
  hcl(h = h, c = 100, l = 65)
}
plotcolor <- plotColorPalettes(length(analyticalSamples)) # the number of colors is the same as how many analytical smples in the data. 

# Create color palette for isobaric label 
iso_color = brewer.pal(9, 'Set1')
```

```{r include=FALSE}
all_spect_title <- list(
  text = "All MS/MS Spectra",
  ##font = f,
  xref = "paper",
  yref = "paper",
  yanchor = "bottom",
  xanchor = "center",
  align = "left",
  x = 0.5,
  y = 1,
  showarrow = FALSE
)

id_spect_title <- list(
  text = "Identified MS/MS Spectra",
  ##font = f,
  xref = "paper",
  yref = "paper",
  yanchor = "bottom",
  xanchor = "center",
  align = "left",
  x = 0.5,
  y = 1,
  showarrow = FALSE
)

all_spect_title_grid <- list(
  text = "All MS/MS Spectra",
  ##font = f,
  xref = "paper",
  yref = "paper",
  yanchor = "bottom",
  xanchor = "center",
  align = "left",
  x = 0.5,
  y = 1.15,
  showarrow = FALSE
)

id_spect_title_grid <- list(
  text = "Identified MS/MS Spectra",
  ##font = f,
  xref = "paper",
  yref = "paper",
  yanchor = "bottom",
  xanchor = "center",
  align = "left",
  x = 0.5,
  y = 1.15,
  showarrow = FALSE
)

# Add new layout annotation for MS/MS Distinct Peptides for Fractions by Analytical Sample (Jiahao)
peptide_title <- list(
  text = "Distinct Peptide",
  ##font = f,
  xref = "paper",
  yref = "paper",
  yanchor = "bottom",
  xanchor = "center",
  align = "left",
  x = 0.5,
  y = 1.0,
  showarrow = FALSE
)

# Add new layout annotation for Redundancy
peptide_rd <- list(
  text = "Peptide Redundancy",
  ##font = f,
  xref = "paper",
  yref = "paper",
  yanchor = "bottom",
  xanchor = "center",
  align = "left",
  x = 0.5,
  y = 1.12,
  showarrow = FALSE
)

# Add new layout annotation for Identified Protein
protein_title <- list(
  text = "Unshared Peptide",
  ##font = f,
  xref = "paper",
  yref = "paper",
  yanchor = "bottom",
  xanchor = "center",
  align = "left",
  x = 0.5,
  y = 1.0,
  showarrow = FALSE
)

# Add new layout annotation for PCA
pca_title <- list(
  text = "PCA",
  ##font = f,
  xref = "paper",
  yref = "paper",
  yanchor = "bottom",
  xanchor = "center",
  align = "left",
  x = 0.5,
  y = 1.0,
  showarrow = FALSE
)
```

```{r, include=FALSE}
grid_arrange_shared_legend <- function(..., ncol = length(list(...)), nrow = 1, position = c("bottom", "right")) {

  plots <- list(...) 
  position <- match.arg(position)
  g <- ggplotGrob(plots[[1]] +theme(legend.position = position))$grobs
  legend <- g[[which(sapply(g, function(x) x$name) == "guide-box")]]
  lheight <- sum(legend$height)
  lwidth <- sum(legend$width)
  gl <- lapply(plots, function(x) x + theme(legend.position="none"))
  gl <- c(gl, ncol = ncol, nrow = nrow)

  combined <- switch(position,
                     "bottom" = arrangeGrob(do.call(arrangeGrob, gl),
                                            legend,
                                            ncol = 1,
                                            heights = unit.c(unit(1, "npc") - lheight, lheight)),
                     "right" = arrangeGrob(do.call(arrangeGrob, gl),
                                           legend,
                                           ncol = 2,
                                           widths = unit.c(unit(1, "npc") - lwidth, lwidth)))
  grid.newpage()
  grid.draw(combined)
  # return gtable invisibly
  invisible(combined)

}

```

```{r}

# make a function to compute the max and min value 
##  Only useful for those has different percentiles
### n and m represent 2 differnt data frame that you want to compare with

find_max<-function(n, m)
{
  max_n <- max(max(subset(n, Percentile <= 95,select=c(value))), max(subset(m, Percentile <= 95,select=c(value))))
  return(max_n)
}

#find_max(QCmetricsLongPrecMW_ALL, QCmetricsLongPrecMW_ID)

find_min <- function(n,m)
{
  min_n <- min(min(subset(n, Percentile <= 95,select=c(value))), min(subset(m, Percentile <= 95,select=c(value))))
  return(min_n)
}

# create title for each of the plot (Jiahao)
title_ALL <- "All MS/MS Spectra" 
title_ID <-  "Identified MS/MS Spectra"

#find_min(QCmetricsLongPrecMW_ALL, QCmetricsLongPrecMW_ID)
```

```{r}

# Build a function for generating the a table with 
## we have 2 parameter one is the kind we want for rows and the other is the dataframe we are sing to generate the table 

##remember to put the "" mark, it only has 2 choices one is fraction and the other one is analytical samples, each kind will generate a pre-determined table

# when kind ==  fraction meaning we are geneating plots whose rows are fractions, like the table of 0 for precursor intensity 

# when kind == analytical sample the rows will be sample names like the table for the percentage of samples under 20 in MS2 per MS2 value

percentage_table <- function(kind, n)
{
  
  B=c(5,25,50,75,95)
  
  # generate a dataframe
  num_row <-  as.numeric(count(unique(select(n, contains(kind)))))
  
  if(kind=="fraction")
  {
    perc_table = matrix(,nrow = length(fractions), ncol = length(B))
  } else 
  {
    if(kind=="analytical")
    {
      perc_table = matrix(,nrow = length(analyticalSamples), ncol = length(B))
    }
  }
  
  if(kind == "fraction"){
    for (i in 1:nrow(perc_table)){
      for (j in 1:length(B)){
        if(sum(n$Fraction == i) > 0)
        {
          perc_table[i,j]<-round(length(which(n$Percentile == B[j] & n$Fraction == i))/length(which(QCmetricsLongPrecInt_ALL$Fraction == i &QCmetricsLongPrecInt_ALL$Percentile == B[j]))*100, 
                                 3)
        }
        else
        {
          perc_table[i,j]<- 0
        }
        
      }
    }
    colnames(perc_table) <- c("5th Perc", "25th Perc", "50th Perc", "75th Perc","95th Perc")
    rownames(perc_table) <- c(paste0("fraction", 1:24))##c(1:25)))
    kable(perc_table)# %>% kable_styling(bootstrap_options = "striped", full_width = F)
    
  }else 
  {
    if(kind == "analytical"){
      for (i in 1:length(analyticalSamples)){
        for(j in 1:length(B)){
          perc_table[i,j] <- round(length(which(n$Percentile == B[j] & n$value <20 & n$analyticalBasename == analyticalSamples[i] ))/ length(which(n$Percentile == B[j] & n$analyticalBasename == analyticalSamples[i]))*100,
                                   3)
        }
      }
      colnames(perc_table) <- c(paste0(B, rep("th Perc", 5)))
      rownames(perc_table) <- c(as.character(analyticalSamples))
      kable(perc_table, caption = "Percent of samples' value less than 20") #%>%
      # kable_styling(bootstrap_options = "striped") 
    }
  }
}

#percentage_table("fraction",QCPrecIntof0_ALL )
```  

```{r}
# Define plot function (Jiahao)
gg_points <- function(data, y_string, x_string,
                   col_string, label_string)
{
  ggplot(data, aes_string(y=y_string, x=x_string, 
                          col=col_string, label=label_string)) +
  geom_point() +
  theme(axis.title.x=element_blank(),
        plot.margin = margin(0.2, 0.5, 0.2, 0, "cm"),
        # axis.text.x=element_blank(),
        legend.position="none")
}

gg_box <- function(data, y_string, x_string,
                   col_string, label_string, label2_string="Fraction",
                   same_scale=FALSE, min_y=NULL, max_y=NULL)
{
  b <- ggplot(data, aes_string(y=y_string, x=x_string, 
                               col=col_string, label=label_string,
                               label2=label2_string)) +
    geom_boxplot()+
    geom_point(alpha=0.6) +
    theme(axis.title.x=element_blank(),
          plot.margin = margin(0.2, 1.0, 0.2, 0, "cm"),
          # axis.text.x=element_blank(),
          legend.position="none")
  if(same_scale)
  {
    b <- b+ylim(min_y, max_y)
  }
  b
}

gg_points_frac <- function(data, y_string, x_string,
                           col_string, label_string, label2_string="Fraction",
                           smooth=FALSE,boxplot=FALSE,                   
                           same_scale=FALSE, min_y=NULL, max_y=NULL)
{
  x_string_fact <- paste("as.factor(",x_string,")",sep="")
  x_string_used = ""
  if(boxplot)
  {
    x_string_used <- x_string_fact
  } else {
    x_string_used <- x_string
  }
  
 
  fractions.unique.orig=unique(data[,x_string])
  fractions.relevel=factor(data[,x_string], levels=ordered(fractions.unique.orig))
  data[,x_string]=fractions.relevel
  
  data.original.level=as.vector(unique(data[, x_string]))
  data[, x_string] = as.numeric(data[, x_string])
  
  
  break.points=as.numeric(unique(data[, x_string]))
  new.break.points=break.points
  if(length(break.points)>6){
    divisor=floor(length(break.points)/4)
    max.x=divisor*4
    new.break.points=break.points[seq(from=1,to=max.x, by=divisor)]
    if(new.break.points[length(new.break.points)]<max(break.points)) new.break.points=c(new.break.points, max(break.points))
  }
  

  pf <- 
 
     ggplot(data, aes_string(y=y_string, x=x_string   # x_string_used
                                , 
                                label=label_string,
                                label2=label2_string
                                ))   +   
    # scale_x_discrete(breaks=break.points, labels=break.points) +
    # scale_x_continuous(breaks=c(1,4,9), labels=c(1,4,9)) +
    scale_x_continuous(breaks = new.break.points, labels = data.original.level[new.break.points]) +
    theme(axis.title.x=element_blank(),
          axis.title.y=element_blank(), #           panel.margin.x=unit(0.5, "lines") , panel.margin.y=unit(1,"lines"), # added 4/12
          plot.margin = margin(0.2, 1.0, 0.2, 0, "cm"),
          legend.position="none")    
      

  if(same_scale)
  {
    pf <- pf+ylim(min_y, max_y)
  }
  if(boxplot)
  {
    pf <- pf+geom_boxplot()
  }
  if(smooth)
  {
    pf <- pf+stat_smooth(aes_string(y=y_string, x=x_string, col=col_string),
                         method="loess", fill="grey50", size=0)
  }
  pf + geom_point(aes_string(col=col_string))
}

gg_points_frac_perc <- function(data, y_string, x_string,
                                col_string, group_string,
                                label_string, label2_string="Fraction",
                                boxplot=FALSE,
                                same_scale=TRUE, min_y=NULL, max_y=NULL)
{
  

  fractions.unique.orig=unique(data[,x_string])
  fractions.relevel=factor(data[,x_string], levels=ordered(fractions.unique.orig))
  data[,x_string]=fractions.relevel
  
  data.original.level=as.vector(unique(data[, x_string]))
  data[, x_string] = as.numeric(data[, x_string])
  
  
  break.points=as.numeric(unique(data[, x_string]))
  new.break.points=break.points
  if(length(break.points)>6){
    divisor=floor(length(break.points)/4)
    max.x=divisor*4
    new.break.points=break.points[seq(from=1,to=max.x, by=divisor)]
    if(new.break.points[length(new.break.points)]<max(break.points)) new.break.points=c(new.break.points, max(break.points))
  }


  
  pfc <- 
     ggplot(data, 
                  aes_string(y=y_string, x=x_string, 
                             col=col_string, group=group_string,
                             label=label_string, label2=label2_string)) + 
        facet_grid(~ Percentile)   +
        scale_x_continuous(breaks = new.break.points, labels=data.original.level[new.break.points]) +
        theme(plot.margin = margin(0.2, 1.0, 0.2, 0, "cm")) #change 
    
  
  if(same_scale){
    pfc <- pfc +  ylim(min_y,max_y)
  }  
  if(boxplot){
    pfc <- pfc + geom_boxplot() +
      theme(axis.title.x=element_blank(),
      #      axis.text.x=element_blank(),
            legend.position="none")
  } else {
    pfc <- pfc +
      theme(legend.position = "none")
  }
  pfc + geom_point(aes_string(col=col_string), alpha=0.6, size=0.9)
}

# Add ggbars
gg_bars <- function(data, y_string, x_string, col_string, label_string)
{
  ggplot(data, aes_string(y=y_string, x=x_string, fill=col_string, label=label_string)) +
  geom_bar(stat = "identity") +
  theme(axis.title.x=element_blank(),
        plot.margin = margin(0.2, 0.5, 0.2, 0, "cm"),
        # axis.text.x=element_blank(),
        legend.title = element_blank()
)
}
```

<P/>
Metrics: <a href="`r basename(QCmetrics_file)`" target="_blank"><b>`r basename(QCmetrics_file)`</b></a>

# - Experimental Design

```{r echo=FALSE,results='asis'}
t <- table(QCmetrics$analyticalBasenameIndex)
mat_t <- matrix(NA, ncol=3, nrow=length(levels(QCmetrics$analyticalBasenameFactor)))
mat_t[,1] <- 1:length(levels(QCmetrics$analyticalBasenameFactor)) 
mat_t[,1] <- sprintf("%02d",mat_t[,1])
mat_t[,2] <- levels(QCmetrics$analyticalBasenameFactor)
mat_t[,3] <- as.matrix(t)[,1]
colnames(mat_t) <- c("Index","Analytical sample", "Fractions")
kable(mat_t) %>% kable_styling(bootstrap_options = "striped", full_width = TRUE)
```
<hr>
<br>

# - Protein Identification 

## - Summary Table 

```{r}
total_ms2_all <- sum(QCmetrics$numofMS2_ALL)
total_ms2_id <- sum(QCmetrics$numofMS2_ID)
identification_per <- paste(round(total_ms2_id / total_ms2_all * 100, 2), "%")
total_peptidecount <- sum(QCmetrics$PeptideCount)
total_protein <- nrow(SUmetrics)

summary_table <- matrix(c(total_ms2_all, total_ms2_id, identification_per, total_peptidecount, total_protein), nrow = 5, ncol = 1)
rownames(summary_table) <- c("Total MS/MS Spectral", "Total MS/MS Spectral Identified", "Identified MS/MS Spectral Coverage", "Total Peptide Count", "Total Protein Identified")
kable(summary_table, align = 'r') %>% kable_styling(bootstrap_options = "striped", full_width = TRUE)
```
<br>

## - Distinct Peptides for Fraction by Analytical Sample

Graph shows box plot of the number of Distinct Peptide Counts across fraction vs. analytical sample. Each analytical sample is represented by a different color. 

```{r}
#(Jiahao)
##get total number of spectra per analytical sample
numofPeptide_ID_per_AS <- tapply(QCmetrics$PeptideCount, INDEX=QCmetrics$analyticalBasename, FUN=sum)
# identical(names(numofPeptide_ALL_per_AS), names(numofPeptide_ID_per_AS))

QCmetrics_AS <- data.frame(analyticalBasename=names(numofPeptide_ID_per_AS),
                           numofPeptide_ID_per_AS=numofPeptide_ID_per_AS)
QCmetrics_AS$`Analytical sample` <- QCmetrics_AS$analyticalBasename

```

```{r,fig.height=2.8, fig.width=9.1}

# get the max and the min number of MS2 peptide counts, including ALL and ID
max_MS2 <- max(QCmetrics$PeptideCount)
min_MS2 <- min(QCmetrics$PeptideCount)


##Get boxplot of number of peptide counts across fractions
g_MS2box_id <- gg_box(QCmetrics, y_string="PeptideCount", x_string="analyticalBasename",
                      col_string="analyticalBasename", label_string="`Analytical sample`")
p_MS2box_id <- ggplotly(g_MS2box_id, tooltip=c("label","label2")) %>% layout(annotations=peptide_title)

subplot(p_MS2box_id, margin=0.05) ##, titleX=TRUE, titleY=TRUE)

```

## - Distinct Peptides for Analytical Sample by Fraction

Graph shows scatter plot of the number of Distinct Peptide Counts across analytical sample vs. fractions. Each analytical sample is represented by a different color. 

```{r,fig.height=3.3, fig.width=9.1}
## Boxplot by Fraction number 
# Reorder Fraction Factor 
#num = table(QCmetrics$analyticalBasenameIndex)[[1]]
#QCmetrics$Fraction <- factor(QCmetrics$Fraction, levels = QCmetrics$Fraction[1:num] )
  
#g_MS2box_id <- gg_box(QCmetrics, y_string="PeptideCount", x_string="Fraction",
#                      col_string="Fraction", label_string="`Analytical sample`")
#p_MS2box_id <- ggplotly(g_MS2box_id, tooltip=c("label","label2")) %>% layout(annotations=peptide_title)

g_DP_byF <- gg_points_frac(QCmetrics,
                               y_string="PeptideCount", x_string="Fraction",
                               col_string="analyticalBasename",
                               label_string = "`Analytical sample`",
                               smooth=TRUE)
p_DP_byF <- ggplotly(g_DP_byF, tooltip=c("label","label2")) %>% layout(annotations=peptide_title)

#subplot(p_MS2box_id, margin=0.05) ##, titleX=TRUE, titleY=TRUE)
subplot(p_DP_byF, margin=0.05) ##, titleX=TRUE, titleY=TRUE)
```

## - Peptides Redundancy Plot for Analytical Sample by Fraction

Graph shows the scatter plot of the 5%,25%,50%,75%,95% for Peptides Redundancy values versus fractions. Each panel is a different percentile. Each analytical sample is represented by a different color. 

```{r,fig.width=9.3, fig.height=3.3}
g_id <- gg_points_frac_perc(filter(QCmetricsPeptideRd, Percentile %in% c(5,25,50,75,95)),
                            y_string = "value",
                            x_string = "Fraction",
                            col_string = "analyticalBasename",
                            group_string="analyticalBasename",
                            label_string="`Analytical sample`",
                            #min_y=find_min(QCmetricsPeptideRd),
                            min_y = min(subset(QCmetricsPeptideRd, Percentile <= 95,select=c(value))),
                            #max_y=find_max(QCmetricsPeptideRd))
                            max_y = max(subset(QCmetricsPeptideRd, Percentile <= 95,select=c(value))))

p_id <- ggplotly(g_id, tooltip=c("label","label2")) %>% layout(annotations=peptide_rd, hovermode = 'compare')

subplot(p_id, margin=0.05)

```

## - Identifided Protein for Analytical Sample

According to the <a href="`r basename(Summary_file)`" target="_blank"><b>`r basename(Summary_file)`</b></a>, there are **`r nrow(Spectral_table)`** proteins identifed. 
Graphs give the number of unshared peptides for all analytical samples. Each sample represented by a different color.

```{r, fig.height=3.3, fig.width=9.1}
# Generate the Plot 
g_id_protein <- gg_points(id_protein, 
                          y_string="ProteinCounts", x_string="analyticalBasename",
                          col_string="analyticalBasename", label_string="`Analytical sample`")
p_id_protein <- ggplotly(g_id_protein, tooltip=c("label")) %>% layout(annotations=protein_title)

subplot(p_id_protein, margin=0.05)##, titleX=TRUE, titleY=TRUE)
```
<hr>
<br>

# - MS/MS Spectra

## - Total MS/MS Spectra by Analytical Sample

Graphs give the total number of MS/MS spectra for the sum of all fractions vs. analytical sample (separate scales for all and identified MS/MS spectra). Each sample represented by a different color.

```{r,fig.height=2.8, fig.width=9}

# get the max and the min number of MS2 spectra, including ALL and ID
max_MS2 <- max(max(QCmetrics_AS$numofMS2_ALL_per_AS), max(QCmetrics_AS$numofMS2_ID_per_AS))
min_MS2 <- min(min(QCmetrics_AS$numofMS2_ALL_per_AS), min(QCmetrics_AS$numofMS2_ID_per_AS))

##Get plot of number of spectra
g_MS2box_all <- gg_points(QCmetrics_AS, 
                          y_string="numofMS2_ALL_per_AS", x_string="analyticalBasename",
                          col_string="analyticalBasename", label_string="`Analytical sample`")
p_MS2box_all <- ggplotly(g_MS2box_all, tooltip=c("label")) %>% layout(annotations=all_spect_title)

##Get plot of number of spectra
g_MS2box_id <- gg_points(QCmetrics_AS, 
                         y_string="numofMS2_ID_per_AS", x_string="analyticalBasename",
                         col_string="analyticalBasename", label_string="`Analytical sample`")
p_MS2box_id <- ggplotly(g_MS2box_id, tooltip=c("label")) %>% layout(annotations=id_spect_title)

subplot(p_MS2box_all,p_MS2box_id, margin=0.05)##, titleX=TRUE, titleY=TRUE)
```

## - MS/MS Spectra for Fractions by Analytical Sample

Graphs show boxplots of the number of MS/MS spectra for individual fraction vs. analytical sample (separate scales for all and identified MS/MS spectra). Each sample is represented by a different color.

```{r, fig.width=9.3, fig.height=2.8}

# get the max and the min number of MS2 spectra, including ALL and ID
max_MS2 <- max(max(QCmetrics$numofMS2_ALL), max(QCmetrics$numofMS2_ID))
min_MS2 <- min(min(QCmetrics$numofMS2_ALL), min(QCmetrics$numofMS2_ID))


##Get boxplot of number of spectra across fractions
g_MS2box_all <- gg_box(QCmetrics, y_string="numofMS2_ALL", x_string="analyticalBasename",
                       col_string="analyticalBasename", label_string="`Analytical sample`")
p_MS2box_all <- ggplotly(g_MS2box_all, tooltip=c("label","label2")) %>% layout(annotations=all_spect_title)

##Get boxplot of number of spectra across fractions
g_MS2box_id <- gg_box(QCmetrics, y_string="numofMS2_ID", x_string="analyticalBasename",
                      col_string="analyticalBasename", label_string="`Analytical sample`")
p_MS2box_id <- ggplotly(g_MS2box_id, tooltip=c("label","label2")) %>% layout(annotations=id_spect_title)

subplot(p_MS2box_all,p_MS2box_id, margin=0.05)##, titleX=TRUE, titleY=TRUE)

```

## - MS/MS Spectra for Analytical Samples by Fraction

Graphs shows a scatter plot of the number of MS/MS spectra for reach analytical sample vs. fraction (separate scales for all and identified MS/MS spectra). Each sample is represented by a different color. The grey area represents the 95% confidence interval for each sample when fitting the default smooth curves.

```{r, fig.height=2.8, fig.width=9.3}
g_MS2sca_all <- gg_points_frac(QCmetrics,
                               y_string="numofMS2_ALL", x_string="Fraction",
                               col_string="analyticalBasename",
                               label_string = "`Analytical sample`",
                               smooth=TRUE)
p_MS2sca_all <- ggplotly(g_MS2sca_all, tooltip=c("label","label2")) %>% layout(annotations=all_spect_title)

g_MS2sca_id <- gg_points_frac(QCmetrics,
                               y_string="numofMS2_ID", x_string="Fraction",
                               col_string="analyticalBasename",
                               label_string = "`Analytical sample`",
                               smooth=TRUE)
p_MS2sca_id <- ggplotly(g_MS2sca_id, tooltip=c("label","label2"))  %>% layout(annotations=id_spect_title)

subplot(p_MS2sca_all, p_MS2sca_id, margin=0.05)


```

## - MS/MS Spectra per Cycle for Analytical Samples by Fraction

Graphs show scatter plots of the 5%,25%,50%,75%,95% percentiles for MS/MS per MS1 values vs. fractions (same scale for all and identified MS/MS spectra). Each panel is a different percentile. Each analytical sample is represented by a different color. *Note: the missing points in 5% are due to missing (zero) precursor intensity values in the mzML file.*

```{r,fig.width=9.3, fig.height=2.8}
g_all <- gg_points_frac_perc(filter(QCmetricsLongMS2perMS_ALL, Percentile %in% c(5,25,50,75,95)),
                             y_string = "value",
                             x_string = "Fraction",
                             col_string = "analyticalBasename",
                             group_string="analyticalBasename",
                             label_string="`Analytical sample`",
                             min_y=find_min(QCmetricsLongMS2perMS_ALL, QCmetricsLongMS2perMS_ID),
                             max_y=find_max(QCmetricsLongMS2perMS_ALL, QCmetricsLongMS2perMS_ID))
p_all <- ggplotly(g_all, tooltip=c("label","label2")) %>% layout(annotations=all_spect_title_grid)

g_id <- gg_points_frac_perc(filter(QCmetricsLongMS2perMS_ID, Percentile %in% c(5,25,50,75,95)),
                            y_string = "value",
                            x_string = "Fraction",
                            col_string = "analyticalBasename",
                            group_string="analyticalBasename",
                            label_string="`Analytical sample`",
                            min_y=find_min(QCmetricsLongMS2perMS_ALL, QCmetricsLongMS2perMS_ID),
                            max_y=find_max(QCmetricsLongMS2perMS_ALL, QCmetricsLongMS2perMS_ID))
p_id <- ggplotly(g_id, tooltip=c("label","label2")) %>% layout(annotations=id_spect_title_grid)

subplot(p_all, p_id, margin=0.05)

min.ms2perms1=find_min(QCmetricsLongMS2perMS_ALL, QCmetricsLongMS2perMS_ID)
# if(min.ms2perms1==0){cat("The missing points in are due to missing (zero) precursor intensity values in the mzML file")}

```
<hr>
<br>

# - MS Precursor 

## - Precursor Intensity for Analytical Samples by Fraction

Graphs show scatter plots of the 5%,25%,50%,75%,95% percentiles for log10(precursor intensity) values vs. fraction (same scale for all and identified MS/MS spectra). Each panel is a different percentile. Each analytical sample is represented by a different color.

```{r, fig.width=9.3, fig.height=2.8}
# get the smallest and the largest value for all and identified seperately to help set the axis range
# Important! Shaojun add 0.5 value to the min and max value to advoid not ploting the points correctly

Pmin_ALL <- log10(min(QCmetricsLongPrecInt_ALL$value[QCmetricsLongPrecInt_ALL$value > 0])) - 0.5
Pmax_ALL <- log10(max(subset(QCmetricsLongPrecInt_ALL, Percentile <= 95,select=c(value)))) + 0.5
Pmin_ID <- log10(min(QCmetricsLongPrecInt_ID$value[QCmetricsLongPrecInt_ID$value > 0]))    - 0.5
Pmax_ID <- log10(max(subset(QCmetricsLongPrecInt_ID, Percentile <= 95,select=c(value))))   + 0.5


QCmetricsLongPrecInt_ALL$value2 <- QCmetricsLongPrecInt_ALL$value
QCmetricsLongPrecInt_ALL$value2[QCmetricsLongPrecInt_ALL$value2 == 0] <-
  min(QCmetricsLongPrecInt_ALL$value2[QCmetricsLongPrecInt_ALL$value2 > 0])*0.5

g_PIsca_all <- gg_points_frac_perc(filter(QCmetricsLongPrecInt_ALL, Percentile %in% c(5,25,50,75,95)),
                                   y_string = "log10(value2)",
                                   x_string = "Fraction",
                                   col_string = "analyticalBasename",
                                   group_string="analyticalBasename",
                                   label_string="`Analytical sample`",
                                   min_y=min(Pmin_ALL,Pmin_ID),
                                   max_y=max(Pmax_ALL, Pmax_ID))
  
p_PIsca_all <- ggplotly(g_PIsca_all, tooltip=c("label","label2")) %>% layout(annotations=all_spect_title_grid)

QCmetricsLongPrecInt_ID$value2 <- QCmetricsLongPrecInt_ID$value
QCmetricsLongPrecInt_ID$value2[QCmetricsLongPrecInt_ID$value2 == 0] <-
  min(QCmetricsLongPrecInt_ID$value2[QCmetricsLongPrecInt_ID$value2 > 0])*0.5

#CAUTION!!!!In this case we've rename the column and may change the result
#colnames(QCmetricsLongMS2Charge_ID)[6] <- "value"

# Or, we might not need to change the variable name
g_PIsca_id <- gg_points_frac_perc(filter(QCmetricsLongPrecInt_ID, Percentile %in% c(5,25,50,75,95)),
                                  y_string = "log10(value2)",
                                  x_string = "Fraction",
                                  col_string = "analyticalBasename",
                                  group_string="analyticalBasename",
                                  label_string="`Analytical sample`",
                                  min_y=min(Pmin_ALL,Pmin_ID),
                                  max_y=max(Pmax_ALL, Pmax_ID))
p_PIsca_id <- ggplotly(g_PIsca_id, tooltip=c("label","label2")) %>% layout(annotations=id_spect_title_grid)

subplot(p_PIsca_all, p_PIsca_id, titleY=TRUE, margin=0.05) #change


```

## - Precursor m/z for Analytical Samples by Fraction

Graphs show scatter plots of the 5%,25%,50%,75%,95% percentiles for precursor m/z values vs. fraction (same scale for all and identified MS/MS spectra). Each panel is a different percentile. Each analytical sample is represented by a different color.

```{r,fig.width=9.3, fig.height=2.8}
g_all <- gg_points_frac_perc(filter(QCmetricsLongPrecMZ_ALL, Percentile %in% c(5,25,50,75,95)),
                             y_string = "value",
                             x_string = "Fraction",
                             col_string = "analyticalBasename",
                             group_string="analyticalBasename",
                             label_string="`Analytical sample`",
                             min_y=find_min(QCmetricsLongPrecMZ_ALL, QCmetricsLongPrecMZ_ID),
                             max_y=find_max(QCmetricsLongPrecMZ_ALL, QCmetricsLongPrecMZ_ID))
p_all <- ggplotly(g_all, tooltip=c("label","label2")) %>% layout(annotations=all_spect_title_grid)

g_id <- gg_points_frac_perc(filter(QCmetricsLongPrecMZ_ID, Percentile %in% c(5,25,50,75,95)),
                            y_string = "value",
                            x_string = "Fraction",
                            col_string = "analyticalBasename",
                            group_string="analyticalBasename",
                            label_string="`Analytical sample`",
                            min_y=find_min(QCmetricsLongPrecMZ_ALL, QCmetricsLongPrecMZ_ID),
                            max_y=find_max(QCmetricsLongPrecMZ_ALL, QCmetricsLongPrecMZ_ID))
p_id <- ggplotly(g_id, tooltip=c("label","label2")) %>% layout(annotations=id_spect_title_grid)

subplot(p_all, p_id, margin=0.05)
```

## - Precursor Molecular Weight for Analytical Samples by Fraction

Graphs show scatter plots of the 5%,25%,50%,75%,95% percentiles for precursor molecular weight values vs. fraction (same scale for all and identified MS/MS spectra). Each panel is a different percentile. Each analytical sample is represented by a different color.

```{r,fig.width=9.3, fig.height=2.8}
g_all <- gg_points_frac_perc(filter(QCmetricsLongPrecMW_ALL, Percentile %in% c(5,25,50,75,95)),
                             y_string = "value",
                             x_string = "Fraction",
                             col_string = "analyticalBasename",
                             group_string="analyticalBasename",
                             label_string="`Analytical sample`",
                             min_y=find_min(QCmetricsLongPrecMW_ALL, QCmetricsLongPrecMW_ID),
                             max_y=find_max(QCmetricsLongPrecMW_ALL, QCmetricsLongPrecMW_ID))
p_all <- ggplotly(g_all, tooltip=c("label","label2")) %>% layout(annotations=all_spect_title_grid)

g_id <- gg_points_frac_perc(filter(QCmetricsLongPrecMW_ID, Percentile %in% c(5,25,50,75,95)),
                            y_string = "value",
                            x_string = "Fraction",
                            col_string = "analyticalBasename",
                            group_string="analyticalBasename",
                            label_string="`Analytical sample`",
                            min_y=find_min(QCmetricsLongPrecMW_ALL, QCmetricsLongPrecMW_ID),
                            max_y=find_max(QCmetricsLongPrecMW_ALL, QCmetricsLongPrecMW_ID))
p_id <- ggplotly(g_id, tooltip=c("label","label2")) %>% layout(annotations=id_spect_title_grid)

subplot(p_all, p_id, margin=0.05)

```

## - Overall Precursor Charge State Distribution

Graphs show the proportion of charge states for MS/MS spectra (same scale for all and identified MS/MS spectra). Each charge state is represented by a different color.
<!--
```{r, fig.width=9.3, fig.height=2.8}


min_ratio <- min(chargestateratio_ALL, chargestateratio_ID)
max_ratio <- max(chargestateratio_ALL, chargestateratio_ID)

g_chargeratio_all <- ggplot(Chargeratio_ALL, aes(x=chargestate, y=chargestateratio_ALL)) +
  geom_bar(stat="identity", aes(fill = chargestate)) +
  geom_text(aes(label = round(chargestateratio_ALL,3)), vjust=-0.3, size=4) +
  scale_color_manual (values = c(plotcolor), name = "Analytical Sample") +
  #stat_smooth(method="loess", fill="grey50", size=0)+
  scale_fill_discrete(name = "Charge State") +
  ggtitle(title_ALL) +
  xlab("MS2 charge state") + ylab("Proportion") +
  ylim(0, max_ratio*1.05) +
  theme(axis.text.x= element_text(angle = 0)) +
  theme(legend.position="none",
        plot.title = element_text(hjust=0.5))

g_chargeratio_ID <- ggplot(Chargeratio_ID, aes(y=chargestateratio_ID, x=chargestate)) +
  geom_bar(stat="identity",aes(fill = chargestate)) +
  geom_text(aes(label = round(chargestateratio_ID,3)), vjust=-0.3, size=4) +
  scale_color_manual (values = c(plotcolor), name = "Analytical Sample") +
  #stat_smooth(method="loess", fill="grey50", size=0)+
  scale_fill_discrete(name = "Charge State") +
  ggtitle(title_ID) +
  xlab("MS2 charge state") + ylab("Proportion") +
  ylim(0, max_ratio*1.05) +
  theme(axis.text.x= element_text(angle = 0)) +
  theme(legend.position="none",
        plot.title = element_text(hjust=0.5))

#grid_arrange_shared_legend(g_chargeratio_all, g_chargeratio_ID, ncol=2)
#subplot(g_chargeratio_all, g_chargeratio_ID, margin=0.05)
```
<hr>
<br>
-->

```{r,fig.height=3.4, fig.width=9}
##Get plot of number of spectra
g_cr_id <- gg_bars(Chargeratio_ID, 
                          y_string="chargestateratio_ID", x_string="chargestate",
                          col_string="chargestate", label_string="`Proportion`")
p_cr_id <- ggplotly(g_cr_id, tooltip=c("label")) %>% layout(annotations=id_spect_title, legend=list(orientation = "h", x = 0.25, y = -0.5, xanchor = "left", yanchor = "bottom"))

##Get plot of number of spectra
g_cr_all <- gg_bars(Chargeratio_ALL, 
                         y_string="chargestateratio_ALL", x_string="chargestate",
                         col_string="chargestate", label_string="`Proportion`")
p_cr_all <- ggplotly(g_cr_all, tooltip=c("label")) %>% layout(annotations=all_spect_title)

subplot(style(p_cr_all, showlegend = FALSE), style(p_cr_id, showlegend = TRUE), margin=0.05)##, titleX=TRUE, titleY=TRUE)
```
<hr>
<br>

# - Chromatography

## - Retention Time Percentiles for Analytical Sample by Fraction

Graphs show scatter plots of the 5%,25%,50%,75%,95% percentiles for spectra retention time of each sample vs. fractions (same scale for all and identified MS/MS spectra). Each panel is a different percentile. Each analytical sample is represented by a different color.

```{r,fig.width=9.3, fig.height=2.8}
g_all <- gg_points_frac_perc(filter(QCmetricsPeptideRT_ALL, Percentile %in% c(5,25,50,75,95)),
                            y_string = "value",
                            x_string = "Fraction",
                            col_string = "analyticalBasename",
                            group_string="analyticalBasename",
                            label_string="`Analytical sample`",
                            min_y=find_min(QCmetricsPeptideRT_ALL, QCmetricsPeptideRT_ID),
                            #min_y = min(subset(QCmetricsPeptideRT_ALL, Percentile <= 95,select=c(value))),
                            max_y=find_max(QCmetricsPeptideRT_ALL, QCmetricsPeptideRT_ID))
                            #max_y = max(subset(QCmetricsPeptideRT_ALL, Percentile <= 95,select=c(value))))

p_all <- ggplotly(g_all, tooltip=c("label","label2")) %>% layout(annotations=all_spect_title_grid)

g_id <- gg_points_frac_perc(filter(QCmetricsPeptideRT_ID, Percentile %in% c(5,25,50,75,95)),
                            y_string = "value",
                            x_string = "Fraction",
                            col_string = "analyticalBasename",
                            group_string="analyticalBasename",
                            label_string="`Analytical sample`",
                            min_y=find_min(QCmetricsPeptideRT_ALL, QCmetricsPeptideRT_ID),
                            #min_y = min(subset(QCmetricsPeptideRT_ID, Percentile <= 95,select=c(value))),
                            max_y=find_max(QCmetricsPeptideRT_ALL, QCmetricsPeptideRT_ID))
                            #max_y = max(subset(QCmetricsPeptideRT_ID, Percentile <= 95,select=c(value))))

p_id <- ggplotly(g_id, tooltip=c("label","label2")) %>% layout(annotations=id_spect_title_grid)

subplot(p_all, p_id, margin=0.05)

```
<hr>
<br>

# - Batch Effect Analysis

## - PCA plot by Analytical Sample

Graph shows the cluster pattern determined by the first two principal components. Each sample represented by a different color.

```{r, fig.width=9, fig.height=9.5}
# Generate the Plot 
test_batch <- as.data.frame(t(s_metrics))  # Use matrix without NAs
test_pca <- prcomp(test_batch, scale.=TRUE)

df_out <- as.data.frame(test_pca$x)
df_out$`Analytical sample` <- batch
df_out$`Biological label` <- gsub('\\..*', '',rownames(df_out))
percentage <- round(test_pca$sdev / sum(test_pca$sdev) * 100, 2)
percentage <- paste( colnames(df_out), "(", paste( as.character(percentage), "%", ")", sep="") )
x_per <- list(title = percentage[1], titlefont = list(size = 13))
y_per <- list(title = percentage[2], titlefont = list(size = 13))
p<-ggplot(df_out,aes(x=PC1,y=PC2,color=`Analytical sample`, text = paste('Biological sample:', `Biological label`)))
p<-p+geom_point()

p_pca_b <- ggplotly(p, tooltip=c("text")) %>% layout(annotations = pca_title, xaxis = x_per, yaxis = y_per, showlegend=FALSE)
  # , legend=list(orientation = "v",x = 5, y = 4, xanchor = "left", yanchor = "bottom"))

p_pca_b
```

## - PCA plot by Isobaric Label 

According to the <a href="`r basename(tmt10_file)`" target="_blank"><b>`r basename(tmt10_file)`</b></a>, Each analytical sample contains **9** biological samples labeled by TMT10. Graph shows the cluster pattern determined by the first two principal components. Each isobaric label represented by a different color.

```{r, fig.width=9, fig.height=9.5}
# Generate index of isobaric label 
iso_lab <- rep(c(1:9), length(mat_t[,1]))
df_out$`Isobaric Label` <- as.factor(iso_lab)

# Generate the plot
p2<-ggplot(df_out,aes(x=PC1,y=PC2,color=`Isobaric Label`, text = paste('Biological sample:', `Biological label`)))
p2<-p2+geom_point()+scale_colour_manual(values=iso_color)
p_pca_b2 <- ggplotly(p2, tooltip=c("text")) %>% layout(annotations = pca_title, xaxis = x_per, yaxis = y_per, showlegend=FALSE , legend=list(orientation = "h", x = 0.18, y = -0.15, xanchor = "left", yanchor = "bottom"))

p_pca_b2
```
<hr>


<font size="2">*For more information about **Plotly Modebar**, click <a href="https://help.plot.ly/getting-to-know-the-plotly-modebar/" target="_blank"><b>here</b></a>.*</font>


<!--Javascript-->
<!--Show(scroll to left)/Hide(scroll to right) TOC-->
<script>
var lastPos = 0;
$(window).scroll(function() {
    var currPos = $(document).scrollLeft();
    if (lastPos < currPos) 
    {$('#TOC').css('opacity', 0);} 
    if (lastPos > currPos) 
    {$('#TOC').css('opacity', 1);}
    lastPos = currPos;
});
</script>